---
title: "Untitled"
author: "Léo"
date: 'Dernière mise à jour : `r format(Sys.time(), "%d %B, %Y")`'
fontfamily: helvetica
fontsize: 50pt
output:
  html_document:
    code_download: no
    code_folding: hide
    df_print: paged
    highlight: tango
    number_sections: yes
    theme: yeti
    toc: yes
    toc_depth: 4
    toc_float:
      collapsed: yes
      smooth_scroll: no
    anchor_sections: no
    fig_width: 7
    fig_height: 4
  pdf_document:
    toc: yes
    toc_depth: '4'
subtitle: v1
---
---

## Packages
```{r message=FALSE, warning=FALSE}
library(gridExtra)
library(cowplot)
library(ggplot2)
library(ggpubr)
library(FactoMineR)
library(factoextra)
library(ggsignif)
library(corrplot)
library(tidyr)
library(viridis)
library(dplyr)
library(seewave)
library(tuneR)
library(soundgen)
library(stringr)
library(tuneR)
library(forcats)
library(uwot)
library(htmlwidgets)
library(chisq.posthoc.test)
library(multcomp)
library(RVAideMemoire)
library(sjPlot)
library(brms)
library(rstan)
```

# Data loading
```{r}
encounters = read.table("D:/encounters/data_merged.csv", header = T, sep = ';', dec = ".")

data = subset(encounters, End.Time..s. < 599)
data = subset(data, Tonality > 0.25 & Score > 0.55)

# On ne garde que les meetings
data$situation = as.factor(data$situation)
data$familiarity = as.factor(data$familiarity)
data$same_diff_sex = as.factor(data$same_diff_sex)
dm = subset(data, situation == "unfam-meet" | situation == "fam-meet")
sex_fam = paste(dm$familiarity, dm$sexes, sep = "_")
dm = cbind(dm, sex_fam)
dm$sex_fam = as.factor(dm$sex_fam)

dm = subset(dm, voc_type != 'other')
dm = subset(dm, voc_type != 'overlaped_calls')
dm = subset(dm, same_diff_sex == 'Diff' | (same_diff_sex == 'Same' & voc_type != 'trill'))
dm = subset(dm, same_diff_sex == 'Diff' | (same_diff_sex == 'Same' & voc_type != 'longdown_trill'))
timeclass = as.integer(dm$Begin.Time..s./60)
dm = cbind(dm, timeclass)

d2m = subset(dm, End.Time..s. < 180 & End.Time..s.> 0)
d2m$timeclass = (as.integer(d2m$Begin.Time..s./20)) * 20

dm$voc_type[dm$voc_type=='complex'] = 'modulated'
dm$voc_type[dm$voc_type=='Down'] = 'down'
```

# Nombre de vocalisations 

```{r}
# on regarde pour chaque rencontre
total_counts <- dm %>%
  group_by(individuals, sex_fam) %>%
  summarize(total_vocalizations = n())

se <- aggregate(total_vocalizations ~ sex_fam, data = total_counts, FUN = function(x) {sqrt(var(x) / length(x))})
mean_nvocs_encounters = aggregate(total_vocalizations ~ sex_fam, data = total_counts, FUN = mean)
mean_nvocs_encounters$lwr = -se$total_vocalizations
mean_nvocs_encounters$upr = se$total_vocalizations
mean_nvocs_encounters$sex_fam = fct_relevel(mean_nvocs_encounters$sex_fam, 
                                            "Fam_FF","Fam_MM", "Fam_MF", "Unfam_FF", "Unfam_MM", "Unfam_MF")
mean_nvocs_encounters$confletters = c("a", "a", "a", "b", "a", "b")
mean_nvocs_encounters$n = c("n = 6", "n = 6", "n = 6", "n = 6", "n = 15", "n = 6")

nicelabs = c("Familiar\nfemales", "Familiar\nmales", "Familiar\nmales and females", "Unfamilar\nfemales", "Unfamilar\nmales", "Unfamilar\nmales and females")

ggplot(mean_nvocs_encounters) +
  geom_bar(aes(x=sex_fam, y=total_vocalizations, fill = sex_fam), stat="identity", alpha=0.7) +
  scale_fill_manual(values = c("Fam_FF" = "#8ecae6",
                              "Fam_MM"="#8ecae6",
                              "Fam_MF"="#8ecae6",
                              "Unfam_FF" = "#126782",
                              "Unfam_MM"="#126782",
                              "Unfam_MF"="#126782"))+
  scale_x_discrete(labels= nicelabs) +
  geom_errorbar(aes(x=sex_fam, ymin=total_vocalizations+lwr, ymax=total_vocalizations+upr), 
                width=0.4, color = "#023047", alpha=0.9, size=0.5) +
  geom_jitter(data = total_counts, aes(x = sex_fam, y = total_vocalizations), width = 0.1) +
  geom_text(aes(label = confletters, x = sex_fam, y = 3500), vjust = -1)+
  theme_bw()+
  theme(panel.grid = element_blank()) +
  labs(y = 'Mean number of vocalizations', x = 'Encounter type')+
  ylim(0,4000)+
  theme(legend.position = 'none')

#ggsave(filename = "D:/encounters/all_plots/mean_nvocs_encounters_points.png", width = 7, height = 4)
```



```{r}
hist(total_counts$total_vocalizations, breaks = 20)

# -------------------------- MODEL BUILDING CODE --------------------------
#
mod_nb = brms::brm(total_vocalizations ~ sex_fam, 
                          data = total_counts, family = "gaussian", 
                          warmup = 1000, iter = 3000, 
                          chains = 3, cores = 3,
                          file = 'D:/encounters/all_models/mod_nb.rds')
# 
summary(mod_nb)
# 
plot(mod_nb, variable = c('b_Intercept', 'b_sex_famUnfam_MF'))
# 
pp_check(mod_nb)
# 
plot(conditional_effects(mod_nb), points = F)
# 
#
#  ------------------------------------------------------------------------


# fitted values 
newdata = data.frame(sex_fam = c("Fam_FF","Fam_MM", "Fam_MF", "Unfam_FF", "Unfam_MM", "Unfam_MF"))
fit_nb = fitted(mod_nb, newdata = newdata, summary = T, re_formula = NA)
colnames(fit_nb) = c('fit', 'se', 'lwr', 'upr')
pl_nb = cbind(newdata, fit_nb)
pl_nb$lwr[pl_nb$lwr<0] = 200

ggplot(data = pl_nb, aes(x = sex_fam, y = fit, color = sex_fam)) +
  geom_pointrange(aes(ymin = lwr, ymax = upr))

pl_nb$sex_fam = fct_relevel(mean_nvocs_encoutners$sex_fam, 
                                            "Fam_FF","Fam_MM", "Fam_MF", "Unfam_FF", "Unfam_MM", "Unfam_MF")
pl_nb$confletters = c("a", "a", "a", "b", "a", "b")
pl_nb$n = c("n = 6", "n = 6", "n = 6", "n = 6", "n = 15", "n = 6")
  
ggplot(pl_nb) +
  geom_errorbar(aes(x=sex_fam, ymin=lwr, ymax=upr), 
                width=0.4, color = "#023047", alpha=0.9, size=1.2) +
  geom_bar(aes(x=sex_fam, y=fit, fill = sex_fam), stat="identity", alpha=1) +
  scale_fill_manual(values = c("Fam_FF" = "#8ecae6",
                              "Fam_MM"="#8ecae6",
                              "Fam_MF"="#8ecae6",
                              "Unfam_FF" = "#126782",
                              "Unfam_MM"="#126782",
                              "Unfam_MF"="#126782"))+
  geom_text(aes(label = confletters, x = sex_fam, y = upr), vjust = -1)+
  geom_text(aes(label = n, x = sex_fam, y = 0), vjust = -1)+
  theme_bw()+
  theme(panel.grid = element_blank()) +
  labs(y = 'Mean number of vocalizations', x = 'Encounter type')+
  ylim(0,3000)+
  theme(legend.position = 'none')


# ggsave(filename = 'D:/encounters/all_plots/mean_vocs_bayesian.jpeg', width = 7, height = 4)

# contrasts
fit_nb= fitted(mod_nb, 
                  newdata = newdata, 
                  summary = F, re_formula = NA)

ctr_nb = fit_nb[,c(6)]-fit_nb[,c(4)]
mean(ctr_nb) ; quantile(ctr_nb, c(0.025,0.975))

```


# Pourcentage de vocalisations au cours de 10 minutes

## Comparaison des types de rencontre

### Graphique général

On regarde le pourcentage d'utilisation de chaque type de call pour chaque type de rencontre, en général sur les 10 minutes.
```{r}


dm_per = read.table("D:/encounters/data_meetings_percentages.csv", sep = ";", dec = ",", header = T)

dm_per$voc_type[dm_per$voc_type=='complex'] = 'modulated'
dm_per$voc_type[dm_per$voc_type=='Down'] = 'down'

data_new1 <- transform(dm_per, perc = ave(n, sex_fam, FUN = prop.table))

data_new1$sex_fam = data_new1$sex_fam = fct_relevel(data_new1$sex_fam,"Unfam_MF","Fam_MF","Unfam_FF","Fam_FF","Unfam_MM", "Fam_MM")
data_new1$voc_type = data_new1$voc_type = fct_relevel(data_new1$voc_type, "longdown_trill", "longdown", "trill", "down" ,"modulated", "up" , "flat")

percentages = aggregate(n~sex_fam+voc_type, data_new1, FUN = sum)
per <- transform(percentages, perc = ave(n, sex_fam, FUN = prop.table))

ggplot(data = per, aes(x = perc, y = sex_fam, fill = voc_type, color = voc_type)) + 
  geom_bar(stat = "identity") +
  scale_fill_manual(values = c("flat" = "#ff595e",
                              "up"="#ff924c",
                              "modulated"="#FFCA3A",
                              "down" = "#A9B858",
                              "trill"="#52A675",
                              "longdown"="#1982c4",
                              "longdown_trill"="#6A4C93")) +
  scale_color_manual(values = c("flat" = "#ff595e",
                              "up"="#ff924c",
                              "modulated"="#FFCA3A",
                              "down" = "#A9B858",
                              "trill"="#52A675",
                              "longdown"="#1982c4",
                              "longdown_trill"="#6A4C93")) +
  labs(title = "Call types repartition per encounter type", y = "Encounter", x = "Percentage of calls") +
  guides(fill=guide_legend(title="Vocalization type"))+
  theme_classic() 



ggsave(filename = "D:/encounters/all_plots/voc_type_repartition.png", width = 10, height = 7)
```
# UMAPS 

```{r}
files = list.files('D:/encounters/all_datasets/umaps/', full.names = T)
i = 1 
for (f in files) {
  umap_df = read.table(f, sep = ',', dec = '.', header = T)
  umap_df = umap_df[sample(1:nrow(umap_df), 2000),]
  plot =
  ggplot(data = umap_df, aes(x = x, y = y, color = label)) +
    geom_point() +
    scale_color_manual(values = c("flat" = "#ff595e",
                            "up"="#ff924c",
                            "complex"="#FFCA3A",
                            "down" = "#A9B858",
                            "trill"="#52A675",
                            "longdown"="#1982c4",
                            "longdown_trill"="#6A4C93")) +
    theme_nothing()
  print(plot)
  # ggsave(paste0("D:/encounters/all_plots/10min_profile_", list.files('D:/encounters/all_datasets/umaps/')[i], ".jpg"),
  #       height = 4, width = 4)
  i = i+1
    
  
}

```


# Par type de rencontre 

```{r warning=FALSE}
# creation du code couleur : 


for (i in seq_len(length(unique(dm$sex_fam)))) {
  
  dsf = subset(dm, dm$sex_fam == as.character(unique(dm$sex_fam))[i])
  dm_tc = aggregate(ID~voc_type+timeclass, data = dsf, FUN = NROW)
  dm_tc_per = transform(dm_tc, perc = ave(ID, timeclass, FUN = prop.table))
  names(dm_tc_per) <- c('voc_type', 'Time', 'N', 'perc')
  dm_tc_per$voc_type = fct_relevel(dm_tc_per$voc_type, "flat", "up", "modulated", "down", "trill", "longdown", "longdown_trill")
  
  p_stacked_bp = ggplot(data = dm_tc_per, aes(x=Time)) +
    geom_bar(aes(y=perc, fill = voc_type), stat="identity") +
    scale_fill_manual(values = c("flat" = "#ff595e",
                                "up"="#ff924c",
                                "modulated"="#FFCA3A",
                                "down" = "#A9B858",
                                "trill"="#52A675",
                                "longdown"="#1982c4",
                                "longdown_trill"="#6A4C93")) +
    labs(title ="", y = "Percentage of calls", x = "Time (m)") +
    theme_classic() +
    theme(axis.title = element_text(size = 15)) +
    theme(axis.text = element_text(size = 15)) +
    theme(legend.position = "none")

  p_density =  ggplot(dsf, aes(x=Begin.Time..s.)) +
      geom_density(fill="gray")+
    labs(title= unique(dm$sex_fam)[i],x="", y = "")+
    theme_classic() +
    theme(axis.text.x = element_blank(), axis.text.y = element_blank())
  
  print(
  ggdraw() +
    draw_plot(p_stacked_bp, x = 0, y = 0, width = 1, height = 0.8) +
    draw_plot(p_density, x = 0.1, y = 0.72, width = 0.89, height = 0.25)
  )
  
  #ggsave(filename = paste0("D:/encounters/all_plots/10min_profile_", unique(dm$sex_fam)[i], ".jpg"), width = 5)
}

ag_timeclass = aggregate(ID ~ timeclass+sex_fam+voc_type+individuals, data= dm, FUN = length)

hist(ag_timeclass$ID, breaks = 30)
conditional_effects(brm_timeclass)

ag_timeclass_general$timeclass = as.numeric(ag_timeclass_general$timeclass)


```

# stats sur la dyn teporelle
```{r}

# Dynamique sur les 10 minutes
ag_timeclass_general = aggregate(ID ~ timeclass+sex_fam+individuals, data= dm, FUN = length)
hist(ag_timeclass_general$ID, breaks = 30)


ag_timeclass_general <- ag_timeclass_general %>%
  group_by(individuals) %>%
  mutate(perc = ID / sum(ID) * 100)

ggplot(ag_timeclass_general, aes(x = as.factor(ag_timeclass_general$timeclass), y = perc)) +
  geom_boxplot() +
  facet_wrap(~sex_fam)


# -------------------------- MODEL BUILDING CODE --------------------------
#
mod_dyn = brms::brm(perc ~ timeclass * sex_fam, 
                          data = ag_timeclass_general, family = "zero_inflated_asym_laplace", 
                          warmup = 1000, iter = 3000, 
                          chains = 3, cores = 3,
                          file = 'D:/encounters/all_models/mod_dynamique_enc_zi.rds')
# 
summary(mod_dyn)
# 
plot(mod_dyn, variable = c('b_Intercept', 'b_timeclass1'))
# 
pp_check(mod_dyn)
# 
plot(conditional_effects(mod_dyn), points = F)
# 
#
#  ------------------------------------------------------------------------
newdata = aggregate(perc~timeclass+sex_fam, data = ag_timeclass_general, FUN = length)[,c(1,2)]
fit_dyn = fitted(mod_dyn, newdata = newdata, summary = T, re_formula = NA)

ctr_dyn_uFF = as.data.frame(fit_dyn[31,4])
fit_dyn[1]- fit_dyn[2]
fit_dyn[11]- fit_dyn[12]
fit_dyn[21]- fit_dyn[22]
fit_dyn[31,4]- fit_dyn[32,4]
fit_dyn[41,3]- fit_dyn[42,3]
fit_dyn[51,4]- fit_dyn[52,4]

ctr_dyn = rowSums(fit_dyn[,c(56:60)])- rowSums(fit_dyn[,c(51:55)])

 50 + mean(ctr_dyn) ; 50 + quantile(ctr_dyn, c(0.025,0.975))

colnames(fit_dyn) = c('fit', 'se', 'lwr', 'upr')
pl_dyn = cbind(ag_timeclass_general[,1:2], fit_dyn)

ggplot()+
  geom_point(data = pl_dyn, aes(x = timeclass, y = fit, color = sex_fam))

```
# table summary de la dynamique temporelle
```{r}

# en pourcentages
mean_dyn = aggregate(cbind(ID, perc) ~ sex_fam + timeclass, data = ag_timeclass_general, FUN = mean)
sd_dyn = aggregate(cbind(ID, perc) ~ sex_fam + timeclass, data = ag_timeclass_general, 
                   FUN = function(x) {sqrt(var(x) / length(x))})



```


### Statistiques

```{r}
dt = table(dm$voc_type, dm$sex_fam)
rownames(dt) = tolower(rownames(dt))
chi2 = chisq.test(dt) ; chi2
res = chi2$stdres

chipv = chisq.posthoc.test::chisq.posthoc.test(dt, method = "bonferroni")
chipv = subset(chipv, Value == "p values")
chipv = chipv[,-2]
colnames(chipv)[1] = "Vocalisation type"
chipv
x = as.vector(dt)

ggplot(data = per) +
   geom_bar( aes(x = sex_fam, y = perc, fill = voc_type), stat="identity") +
    scale_fill_manual(values = c("flat" = "#ff595e",
                                "up"="#ff924c",
                                "modulated"="#FFCA3A",
                                "down" = "#A9B858",
                                "trill"="#52A675",
                                "longdown"="#1982c4",
                                "longdown_trill"="#6A4C93")) +
    labs(title ="", y = "Percentage of calls", x = "") +
    theme_bw()+
   # theme(axis.title = element_text(size = 15)) +
   #theme(axis.text = element_text(size = 15)) +
    theme(legend.position = "none") +
    facet_wrap(~voc_type)


# avec un modele de vecteur
data_new1$voc_type = as.factor(data_new1$voc_type)
data_calls = data_new1[,c(1:3,5)]
perc_calls <- pivot_wider(data_calls, names_from = voc_type, values_from = perc)
perc_calls = perc_calls[,-2]


hist(data_new1$perc)
perc_calls = perc_calls[-32,]
perc_calls[perc_calls==0] = 2e-16
perc_calls[, -1] <- perc_calls[, -1] / rowSums(perc_calls[, -1])

percentages = aggregate(cbind(flat, up, modulated, down, longdown, trill, longdown_trill) ~ sex_fam, data = perc_calls, FUN = mean)

ggplot(data = data_new1, aes(x = sex_fam, y = perc)) +
  geom_boxplot()+
  facet_wrap(~voc_type)

# -------------------------- MODEL BUILDING CODE --------------------------
#
mod_perc = brms::brm(cbind(flat, up, modulated, down, longdown, trill, longdown_trill) ~ sex_fam, 
                          data = perc_calls, family = 'dirichlet2', 
                          warmup = 500, iter = 4000, 
                          chains = 4, cores = 4,
                          file = 'D:/encounters/all_models/mod_all_perc.rds')
# 
summary(mod_perc)
# 
plot(mod_perc, variable = c('b_Intercept', 'b_sex_famUnfam_MF'))
# 
pp_check(mod_perc, resp = 'modulated')
# 
plot(conditional_effects(mod_perc), points = F)
# 
#
#  ------------------------------------------------------------------------

newdata = data.frame(sex_fam = levels(as.factor(perc_calls$sex_fam)))
fit = fitted(mod_perc, newdata = newdata, robust = T, re_formula = NA, summary = F)



```

# contrasts
```{r}
fit = fitted(mod_perc, newdata = newdata, robust = F, re_formula = NA, summary = T)
j = 1
for (i in as.character(levels(data_new1$voc_type))) {
  # voc = gsub("_", "", i)
  voc = paste0('P(Y = ', i, ')')
  pl_fit_voc = as.data.frame(fit[, , voc])
  pl_fit_voc$voc_type = i
  pl_fit_voc = cbind(newdata, pl_fit_voc)
  if (j==1) {pl_fit = pl_fit_voc}
  else {pl_fit = rbind(pl_fit, pl_fit_voc)}
  j=j+1
}

colnames(pl_fit) = c('sex_fam', 'fit', 'se', 'lwr', 'upr', 'voc_type')
pl_fit$sex_fam = fct_relevel(pl_fit$sex_fam, "Fam_FF","Fam_MM", "Fam_MF", "Unfam_FF", "Unfam_MM", "Unfam_MF")

for (voc in unique(pl_fit$voc_type)) {
  ggplot(data = pl_fit[pl_fit$voc_type==voc,]) +
  geom_pointrange(aes(x = sex_fam, y = fit, ymin = lwr, ymax = upr, col = sex_fam))  +
  scale_color_manual(values = c("Fam_FF" = "#8ecae6",
                              "Fam_MM"="#8ecae6",
                              "Fam_MF"="#8ecae6",
                              "Unfam_FF" = "#126782",
                              "Unfam_MM"="#126782",
                              "Unfam_MF"="#126782"))+
  theme_bw()+
  theme(panel.grid = element_blank()) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(y = 'Mean percentage of vocalizations', x = 'Encounter type', title = voc)+
  theme(legend.position = 'none')+
    scale_y_log10()
  plot(last_plot()) 
  
  # ggsave(paste0('D:/encounters/all_plots/voc_types/', voc, '.png'), width=3)
}

ggplot(data = pl_fit) +
  geom_pointrange(aes(x = sex_fam, y = fit, ymin = lwr, ymax = upr, col = sex_fam))  +
  scale_color_manual(values = c("Fam_FF" = "#8ecae6",
                              "Fam_MM"="#8ecae6",
                              "Fam_MF"="#8ecae6",
                              "Unfam_FF" = "#126782",
                              "Unfam_MM"="#126782",
                              "Unfam_MF"="#126782"))+
  theme_bw()+
  theme(panel.grid = element_blank()) +
  labs(y = 'Mean percentage of vocalizations', x = 'Encounter type')+
  theme(legend.position = 'none') +
  facet_wrap(~voc_type) +
  scale_y_log10()
  
  
```

```{r}


fit = fitted(mod_perc, newdata = newdata, robust = T, re_formula = NA, summary = F)

d = fit[,2,"modulated"] - fit[,5,"modulated"]
mean(d<0)
paste0(round(quantile(d, probs = 0.5), 3), ", 95% CI [", round(quantile(d, probs = 0.025), 3), ", ", round(quantile(d, probs = 0.975), 3), "]")


for (voc in levels(data_new1$voc_type)) {
  
}

```

# barplots

```{r}

new_perc <- pivot_longer(percentages, cols = -sex_fam, names_to = "voc_type", values_to = "perc")
new_perc$voc_type = fct_relevel(new_perc$voc_type, "flat", "up", "modulated", "down", "trill", "longdown", "longdown_trill")

ggplot(data = new_perc, aes(x = perc, y = sex_fam, fill = voc_type, color = voc_type)) + 
  geom_bar(stat = "identity") +
  scale_fill_manual(values = c("flat" = "#ff595e",
                              "up"="#ff924c",
                              "modulated"="#FFCA3A",
                              "down" = "#A9B858",
                              "trill"="#52A675",
                              "longdown"="#1982c4",
                              "longdown_trill"="#6A4C93")) +
  scale_color_manual(values = c("flat" = "#ff595e",
                              "up"="#ff924c",
                              "modulated"="#FFCA3A",
                              "down" = "#A9B858",
                              "trill"="#52A675",
                              "longdown"="#1982c4",
                              "longdown_trill"="#6A4C93")) +
  labs(title = "Call types repartition per encounter type", y = "Encounter", x = "Percentage of calls") +
  guides(fill=guide_legend(title="Vocalisation type"))+
  theme_classic() 
```


```{r}

summary_acoustic = aggregate(cbind(Call.Length..s., Principal.Frequency..kHz., Low.Freq..kHz., High.Freq..kHz.,
                                   Delta.Freq..kHz., Frequency.Standard.Deviation..kHz.)~voc_type, 
                             data = dm, FUN = mean )
colnames(summary_acoustic) = c("Vocalization type", "Duration (ms)", "Principal Frequency (kHz)", "Low Frequency (kHz)",
                               "High Frequency (kHz)", "Frequency Bandwith (kHz)", "Frequency SD (kHz)")
summary_acoustic$`Duration (ms)` = summary_acoustic$`Duration (ms)`*1000

sd_acoustic = aggregate(cbind(Call.Length..s., Principal.Frequency..kHz., Low.Freq..kHz., High.Freq..kHz.,
                                   Delta.Freq..kHz., Frequency.Standard.Deviation..kHz.)~voc_type, 
                             data = dm, FUN = sd )

  
```

# on regarde l'overlap
```{r}
data_overlap = subset(data, voc_type=='overlaped_calls')
table(data_overlap$situation, data_overlap$sexes)

sex_fam = paste(data_overlap$familiarity, data_overlap$sexes, sep = "_")
data_overlap = cbind(data_overlap, sex_fam)

total_counts <- dm %>%
  group_by(sex_fam, individuals) %>%
  summarize(total_vocalizations = n())

overlap_counts <- data_overlap %>%
  group_by(sex_fam, individuals) %>%
  summarize(vocalizations = n())

data_overlap <- total_counts %>%
  left_join(overlap_counts, by = c("sex_fam", "individuals")) %>%
  mutate(vocalizations = ifelse(is.na(vocalizations), 0, vocalizations)) %>%
  mutate(percentage = vocalizations / total_vocalizations)


#se <- aggregate(percentage ~ sex_fam, data = data_overlap, FUN = function(x) {sqrt(var(x) / length(x))})

mean_nvocs_overlap = aggregate(percentage ~ sex_fam, data = data_overlap, FUN = mean)
#mean_nvocs_overlap$se = se$percentage
mean_nvocs_overlap$sex_fam = fct_relevel(mean_nvocs_overlap$sex_fam, 
                                            "Fam_FF","Fam_MM", "Fam_MF", "Unfam_FF", "Unfam_MM", "Unfam_MF")

# bayesian
brm_nvocs_overlap = brm(percentage~sex_fam, 
                        data = data_overlap[data_overlap$percentage!=0,], family = "hurdle_gamma")

conditional_effects(brm_nvocs_overlap)
pp_check(brm_nvocs_overlap)

fit_nvocs_overlap = fitted(brm_nvocs_overlap, 
                           newdata = data.frame(sex_fam = unique(mean_nvocs_overlap$sex_fam)))
colnames(fit_nvocs_overlap) = c('fit', 'se', 'lwr', 'upr')
fit_nvocs_overlap


mean_nvocs_overlap$confletters = c("a", "b", "a", "a", "a", "a")
mean_nvocs_overlap$n = c("n = 6", "n = 6", "n = 6", "n = 6", "n = 15", "n = 6")
mean_nvocs_overlap

mean_nvocs_overlap = cbind(mean_nvocs_overlap, as.data.frame(fit_nvocs_overlap))



conditional_effects(brm_nvocs_overlap)

ggplot(data = mean_nvocs_overlap) +
  geom_pointrange(aes(x=sex_fam, y=fit*100, ymin=lwr*100, ymax=upr*100, color = sex_fam)) +
  scale_color_manual(values = c("Fam_FF" = "#8ecae6",
                              "Fam_MM"="#8ecae6",
                              "Fam_MF"="#8ecae6",
                              "Unfam_FF" = "#126782",
                              "Unfam_MM"="#126782",
                              "Unfam_MF"="#126782"))+
  scale_x_discrete(labels= nicelabs) +
  #geom_text(aes(label = confletters, x = sex_fam, y = percentage+upr), vjust = -1)+
  #geom_text(aes(label = n, x = sex_fam, y = 0), vjust = -1)+
  theme_bw()+
  theme(panel.grid = element_blank()) +
  labs(y = 'Mean percentage of overlap in vocalizations', x = 'Encounter type')+
  theme(legend.position = 'none')

# ggsave(filename = "D:/encounters/all_plots/perc_overlap.jpg", width = 6, height = 4)

# contrasts

fit = fitted(brm_nvocs_overlap, newdata = data.frame(sex_fam = unique(mean_nvocs_overlap$sex_fam)), summary = F)

for (i in 1:6) {
  for (j in 1:6) { 
    d = fit[,i] - fit[,j]
    mean(d<0)
    print(i); print(j)
    print(paste0(round(quantile(d, probs = 0.5), 3)*100, "%, [", round(quantile(d, probs = 0.025), 3)*100, "%, ", round(quantile(d, probs = 0.975), 3)*100, "%]"))
    }
}

duration = aggregate(Call.Length..s.~sex_fam+individuals, data = dm, FUN = sum)

dur_ov = merge(duration, data_overlap, by = 'individuals', all.y = T)

ggplot(data = dur_ov, aes(x=percentage, y=total_vocalizations)) + 
  geom_point()

# bayesian duration
brm_duration = brm(Call.Length..s.~sex_fam, 
                        data = duration, family = "hurdle_gamma")

conditional_effects(brm_duration, points = T)
pp_check(brm_duration)

fit_duration = fitted(brm_duration, 
                           newdata = data.frame(sex_fam = unique(duration$sex_fam)))
colnames(fit_duration) = c('fit', 'se', 'lwr', 'upr')

pl_duration = cbind(data.frame(sex_fam = unique(duration$sex_fam)), fit_duration)

ggplot(data = pl_duration) +
  geom_pointrange(aes(x=fct_relevel(sex_fam, "Fam_FF","Fam_MM","Fam_MF","Unfam_FF","Unfam_MM","Unfam_MF"), y=fit/60, ymin=lwr/60, ymax=upr/60, color = sex_fam)) +
  scale_color_manual(values = c("Fam_FF" = "#8ecae6",
                              "Fam_MM"="#8ecae6",
                              "Fam_MF"="#8ecae6",
                              "Unfam_FF" = "#126782",
                              "Unfam_MM"="#126782",
                              "Unfam_MF"="#126782"))+
  scale_x_discrete(labels= nicelabs) +
  #geom_text(aes(label = confletters, x = sex_fam, y = percentage+upr), vjust = -1)+
  #geom_text(aes(label = n, x = sex_fam, y = 0), vjust = -1)+
  theme_bw()+
  theme(panel.grid = element_blank()) +
  labs(y = 'Total duration of vocalizations\nduring a 10-min trial (min)', x = '')+
  theme(legend.position = 'none')

ggsave(filename = "D:/encounters/all_plots/call_duration_over_trials.jpg", width = 6, height = 4)


```


# Dynamique des calls sur les 10 minutes rencontres / alone

```{r}
hab = readxl::read_excel('D:/separations/all_exports/12_07_23-09_31_45_merged_Stats.xlsx') 
hab$indiv = 0
hab$exp_type = 0
for (i in  1:nrow(hab)) {
  temp = strsplit(strsplit(hab$File[i], split = '\\\\')[[1]][4], split = "\\.")[[1]][1]
  hab$indiv[i] = strsplit(temp, split = '_')[[1]][2]
  hab$exp_type[i] = strsplit(temp, split = '_')[[1]][1]
}
timeclass = as.integer(hab$`Begin Time (s)`/60)
hab$timeclass = timeclass
table(hab$timeclass)


alone = read.table('D:/repertoire/all_datasets/data_alone.csv', header = T, row.names = 1, sep = ';', dec = ',') 
timeclass = as.integer(alone$Begin.Time..s./60)
alone$timeclass = timeclass
table(alone$timeclass)

# on fait la moyenne des densités de vocs pour chaque indiv 
total_counts <- alone %>%
  group_by(indiv) %>%
  summarize(total_vocalizations = n())

timeclass_counts <- alone %>%
  group_by(timeclass, indiv) %>%
  summarize(vocalizations = n())

percentage <- timeclass_counts %>%
  left_join(total_counts, by = "indiv") %>%
  mutate(percentage = vocalizations / total_vocalizations * 100)

average_percentage <- percentage %>%
  group_by(timeclass, indiv) %>%
  summarize(avg_percentage = mean(percentage, na.rm = TRUE))

aggregate(avg_percentage~timeclass, data = average_percentage, FUN = mean)

ggplot() +
  geom_density(data = alone, aes(x = alone$Begin.Time..s.)) +
  geom_density(data = dm[dm$familiarity=='Fam',], aes(x = dm$Begin.Time..s.[dm$familiarity=='Fam'])) +
  geom_density(data = dm[dm$familiarity=='Unfam',], aes(x = dm$Begin.Time..s.[dm$familiarity=='Unfam']))

ggplot(data = alone, aes(x = timeclass)) +
  geom_bar() +
  facet_wrap(~indiv)
```

```{r}


dyn =
data.frame(id = c(alone$indiv, hab$indiv),
           exp_type = c(rep('separation', nrow(alone)), rep('habituation', nrow(hab))), 
           time = c(alone$Begin.Time..s., hab$`Begin Time (s)`))


dyn = subset(dyn, dyn$time<600)
dyn$timeclass = as.integer(dyn$time/60)
ag_dyn = aggregate(time~id+exp_type+timeclass, data = dyn, FUN = length)
colnames(ag_dyn) = c('id', 'exp_type', 'timeclass', 'n')

# Create a data frame with all possible combinations of id, exp_type, and timeclass
all_combinations <- expand.grid(
  id = unique(ag_dyn$id),
  timeclass = 0:9  # Assuming timeclass goes from 0 to 9
)

# Merge the original data frame with the all_combinations data frame
# This will add missing rows with n = 0
result <- merge(all_combinations, ag_dyn, all.x = TRUE)

# Replace NA values in 'n' with 0
result$n[is.na(result$n)] <- 0


# Group by 'id' and 'timeclass', and calculate the sum of 'n' for each group
ag_dyn_sum <- result %>%
  group_by(id, timeclass, exp_type) %>%
  summarise(total_n = sum(n))

# Calculate the sum of 'n' over all time classes for each 'id'
id_total_n <- ag_dyn_sum %>%
  group_by(id) %>%
  summarise(id_total_n = sum(total_n))

# Join the 'id_total_n' back to 'ag_dyn_sum'
ag_dyn_sum <- ag_dyn_sum %>%
  left_join(id_total_n, by = "id")

# Calculate the percentage ('perc') for each 'id', 'timeclass'
ag_dyn_sum$perc <- ag_dyn_sum$total_n / ag_dyn_sum$id_total_n * 100

# If you want to replace NA values in 'perc' with 0 for missing rows, you can do this:
ag_dyn_sum$perc[is.na(ag_dyn$perc)] <- 0

ag_dyn_sum$timeclass = as.numeric(ag_dyn_sum$timeclass)
ggplot(data = ag_dyn_sum, aes(x = timeclass, y = perc, fill = exp_type))+
  geom_boxplot()

hist(ag_dyn_sum$perc, breaks = 100)

ag_dyn_sum$perc=ag_dyn_sum$perc/100

# construction du df avec dimininution 
ag_dyn_sum$dim = 0
for (i in 1:(nrow(ag_dyn_sum)-1)) { 
  if (ag_dyn_sum$timeclass[i] != 0) {
    if (ag_dyn_sum$perc[i] - ag_dyn_sum$perc[ag_dyn_sum$id == ag_dyn_sum$id[i] & ag_dyn_sum$timeclass == 2] < 0) {
      ag_dyn_sum$dim[i] = ((ag_dyn_sum$perc[i] / ag_dyn_sum$perc[ag_dyn_sum$id == ag_dyn_sum$id[i] & ag_dyn_sum$timeclass == 2]) - 1) * 100 }
    else { 
      ag_dyn_sum$dim[i] = ((ag_dyn_sum$perc[i] / ag_dyn_sum$perc[ag_dyn_sum$id == ag_dyn_sum$id[i] & ag_dyn_sum$timeclass == 2]) - 1) * 100 }
  }
}
ag_dyn_sum$dim[is.nan(ag_dyn_sum$dim)] = 0
ag_dyn_sum$dim[ag_dyn_sum$dim == Inf] = 100
ag_dyn_sum$dim[ag_dyn_sum$dim > 100] = 100 

```

# vrai data
```{r}
ggplot(data = ag_dyn_sum) +
  geom_jitter(aes(x = timeclass+1, y = dim, color = exp_type))+
  geom_smooth(aes(x = timeclass+1, y = dim, color = exp_type), method = "glm")+
  theme_bw()+
  theme(panel.grid = element_blank()) +
  labs(y = 'Percentage of change in compare to\nfirst minute of experiment', x = 'Time (min)')+
  guides(color=guide_legend(title="Experiment type")) +
  geom_hline(yintercept = 0, linetype = 2)


# ggsave(filename = "D:/encounters/all_plots/sepVSfam.jpg", width = 6, height = 4)
```


```{r}
hist(ag_dyn_sum$total_n, breaks = 50)

ag_dyn_sum$timeclass = as.factor(ag_dyn_sum$timeclass)
ag_dyn_sum$total_n[ag_dyn_sum$exp_type=='habituation'] = ag_dyn_sum$total_n[ag_dyn_sum$exp_type=='habituation']/2
get_prior(total_n ~ timeclass * exp_type +(1|id),
                    data = ag_dyn_sum, family = "gamma")

# -------------------------- MODEL BUILDING CODE --------------------------
#
mod_dyn = brms::brm(total_n ~ timeclass * exp_type +(1|id),
                    data = ag_dyn_sum, family = "gamma",
                    warmup = 1000, iter = 5000, 
                    chains = 4, cores = 4,
                    file = 'D:/separations/all_models/mod_dyn2.rds')
# 
summary(mod_dyn)
# 
plot(mod_dyn, variable = c('b_Intercept'))
# 
pp_check(mod_dyn)
# 
plot(conditional_effects(mod_dyn), points = F)
# 
#
#  ------------------------------------------------------------------------


# fitted values 
newdata = data.frame(exp_type = c(rep("habituation",10), rep("separation",10)), timeclass = rep(seq(0,9),2))
fit_dyn= fitted(mod_dyn, newdata = newdata, summary = T, re_formula = NA)
colnames(fit_dyn) = c('fit', 'se', 'lwr', 'upr')
pl_dyn = cbind(newdata, fit_dyn)
colnames(pl_dyn)[1] = "Experiment"

pl_dyn$timeclass[pl_dyn$Experiment=='separation'] = pl_dyn$timeclass[pl_dyn$Experiment=='separation']+10

ggplot() +
  geom_pointrange(data = pl_dyn, aes(x = timeclass, y = fit, ymin = lwr, ymax = upr, color = Experiment, shape = Experiment), linetype = 2) +
  geom_smooth(data = pl_dyn, aes(x = timeclass, y = fit, group = Experiment, color = Experiment), method = "loess")+
  geom_vline(aes(xintercept=9.5), linetype="dashed", size = 1 ) +
  scale_colour_manual(name = "Experiment phase",
                      labels = c("Habituation - 2 inds", "Separation - 1 ind"),
                      values = c("#264653", "#2a9d8f")) +   
  scale_shape_manual(name = "Experiment phase",
                      labels = c("Habituation - 2 inds", "Separation - 1 ind"),
                      values = c(17, 19)) +  
  theme_bw()+
  theme(panel.grid = element_blank()) +
  theme(legend.position = c(.82, .85))+
  labs(y = 'Number of vocalization emitted', x = 'Time (min)')
ggsave(filename = 'D:/encounters/all_plots/dyn_encountersVSsep.jpeg', width = 6, height = 4)

# contrasts
fit_dyn= fitted(mod_dyn, 
                  newdata = newdata, 
                  summary = F, re_formula = NA)
ctr_dyn = fit_dyn[,c(20)]-fit_dyn[,c(11)]
mean(ctr_dyn) ; quantile(ctr_dyn, c(0.025,0.975))

fit_dyn = fitted(mod_dyn, newdata = newdata, summary = F, re_formula = NA)
ctr_dyn = rowSums(fit_dyn[,c(1:5)])- rowSums(fit_dyn[,c(6:10)])
50 + mean(ctr_dyn)*100 ; 50 + quantile(ctr_dyn, c(0.025,0.975))*100

fit_dyn = fitted(mod_dyn, newdata = newdata, summary = F, re_formula = NA)
ctr_dyn = rowSums(fit_dyn[,c(11:15)])- rowSums(fit_dyn[,c(16:20)])
50 - mean(ctr_dyn)*100 ; 50-quantile(ctr_dyn, c(0.025,0.975))*100

# mean percentage change for fam encounters 

```
```{r}

hist(dyn$time, breaks = 50)

# -------------------------- MODEL BUILDING CODE --------------------------
#
mod_dyn_continuous = brms::brm(s(time) ~ exp_type,# + (1|id), 
                          data = dyn, family = "student", 
                          warmup = 500, iter = 2000, 
                          chains = 3, cores = 3,
                          file = 'D:/repertoire/all_models/mod_dyn_dim_continuous_s.rds')
# 
summary(mod_dyn_continuous)
# 
plot(mod_dyn, variable = c('b_Intercept', 'b_timeclass1'))
# 
pp_check(mod_dyn_continuous)
# 
plot(conditional_effects(mod_dyn_continuous), points = T)
# 
#
#  ------------------------------------------------------------------------
```

